Acceleration of Derivative Calculations with Application to Radial Basis Function ­ Finite-Differences on the Intel MIC Architecture

### 2014-06-10 slides/2014_ics/slides-ics.tex
first slide on derivative

\begin{frame}
  \frametitle{Derivative as Linear operators}
\end{frame}

@@

\begin{frame}
  \frametitle{Have to use vector operations to get high bandwidth}

  \begin{columns}
    \column{.49\linewidth}

    \begin{center}
      \includegraphics[width=\linewidth,page=1]{slides-figures/PPAM-data/bandwidth.pdf}

      Read
    \end{center}

    \column{.49\linewidth}

    \begin{center}
      \includegraphics[width=\linewidth,page=2]{slides-figures/PPAM-data/bandwidth.pdf}

      Write
    \end{center}

  \end{columns}

  \begin{itemize}
  \item Using the appropriate vectorial instructions gives significant
    improvements.
  \item Read Peak: 183GB/s.
  \item Write Peak: 160GB/s.
  \end{itemize}

  \tiny Source: PPAM 2013
\end{frame}

>>>>

\begin{frame}[fragile]
  \frametitle{Derivative as linear algebra operators}

  \begin{columns}
    \column{.5\linewidth}
    \begin{block}{2nd derivative, 1D}

      \includegraphics[width=\linewidth]{slides-figures/1d.pdf}

      $$u''_i = \frac{u_{i+1}-2u_i+u_{i-1}}{h^2}$$
      \scalebox{.8}{$A = \begin{pmatrix}
        \dots & \dots & \dots & \dots & \dots & \dots & \dots \\
        \dots & 1 & -2 & 1 & 0 & 0 & \dots  \\
        \dots & 0 & 1 & -2 & 1 & 0 & \dots \\
        \dots & 0 & 0 & 1 & -2 & 1 & \dots  \\
        \dots & \dots & \dots & \dots & \dots & \dots & \dots
      \end{pmatrix}$}
      $$u'' = Au$$
    \end{block}

    \column{.49\linewidth}
    \begin{block}{2nd derivative, 2D}
      \begin{center}
        \includegraphics[width=.6\linewidth]{slides-figures/2d.pdf}
      \end{center}

        $L_{i,j} = \bigtriangledown^2 u_{i,j} = \frac{1}{h^2} (u_{i+1,j}  +u_{i-1,j}$

        $~~~~~~~~~~~~~~~~+u_{i,j-1}+u_{i,j+1}-4u_i)$
    \end{block}

@@

% \begin{frame}
%   \frametitle{Have to use vector operations to get high bandwidth}

%   \begin{columns}
%     \column{.49\linewidth}

%     \begin{center}
%       \includegraphics[width=\linewidth,page=1]{slides-figures/PPAM-data/bandwidth.pdf}

%       Read
%     \end{center}

%     \column{.49\linewidth}

%     \begin{center}
%       \includegraphics[width=\linewidth,page=2]{slides-figures/PPAM-data/bandwidth.pdf}

%       Write
%     \end{center}

%   \end{columns}

%   \begin{itemize}
%   \item Using the appropriate vectorial instructions gives significant
%     improvements.
%   \item Read Peak: 183GB/s.
%   \item Write Peak: 160GB/s.
%   \end{itemize}

%   \tiny Source: PPAM 2013
% \end{frame}
